Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms \cite{dc_terms}. There is also the recent Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens. These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. Even so, metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, and serves to justify a new initiative at Tulane University, where staff are manually capturing content for 22 metadata properties, to characterize the quality of digitized specimens drawn from the INHS collection and iDigBio. This current process is costly in terms of labor and time, error-prone, and underscores the need to
explore automatic metadata generation methods.

%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS},

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse.

Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}. Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.

%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} cartographic info.
%above paragraph..need to finesse a couple of sentences w/results, weave in these 2 citations, and then say we can look to image analysis.

@@

\section{Methods}
Our process for metadata generation can be broken into three steps: object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), image processing at the pixel level, and calculations on the results of the previous steps to determine higher level metadata properties.
% \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}

>>>>

Since the digital collections may each contain tens of thousands of images, manually producing additional image quality metadata for each digitized specimen is both labor-and time intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in specimen research image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms \cite{dc_terms}. The Audubon Core\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3-D digitized specimens, is an DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. This point is also emphasized by Wieczorek\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness. Even so, metadata describing image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, serves as the rationale for Tulane University's effort to manually capturing content for 22 metadata properties characterizing digitized specimen image quality. Their work is being conducted in connection with the lager BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
explore automatic metadata generation methods.
%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
\subsection{Automatic Metadata Generation}
Automatic metadata generation advance covering both descriptive and technical metadata are relevant to the research presented in this paper. Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}. Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows. Heidorn, et al,\cite{heidorn2008automatic} demonstrated the use optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings. The extracted information was  encoded in the DwC metadata associated with the specimen's digitized rendering. There's also been some success with extracting descriptive cartographic information from maps \cite{manso2004automatic}. While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited. More significantly, descriptive metadata does not not sufficiently addressed data quality.

Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)\cite{Exif}, the camera's technical metadata that is automatically captured and inserted into digital image files at the time of digitization. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error. Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality images for neural networks and the application of machine learning.

@@

\section{Methods}
Our process for metadata generation can be broken into three steps: 1) object detection with Facebook's Detectron2 machine learning library (subsequently referred to as \verb|detectron|), 2) image processing at the pixel level, and 3) calculations on the results of the previous steps to determine higher level metadata properties.
% \todo{Definitely need to explain somewhere in more detail about our current admissibility criteria for images. Not sure where I want to put it yet so just leaving it as a todo}
